A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-08 01_background.Rmd

This paper refers extensively to the `R` package `atlastools` (Gupte 2020), which can be installed from [Github.](https://github.com/pratikunterwegs/atlastools).

@@

The build status of the 'Master' branch is shown here.

>>>>

This paper refers extensively to the `R` package `atlastools` (Gupte 2020), which can be installed from [Github](https://github.com/pratikunterwegs/atlastools).

@@

The build status of the 'Master' branch is shown here:

### 2020-10-08 05_calibration_data.Rmd

```{r}
# read and plot example data
data <- fread("data/atlas1060_allTrials_annotated.csv")
data_raw <- copy(data)
# plot data
fig_data_raw <-
  ggplot(data)+
  geom_path(aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(aes(x, y),
             col = "steelblue", alpha = 0.2, size = 2)+
  ggthemes::theme_map()+
  coord_sf(crs = 32631)

@@

@@

```{r}
# get linear model
model_duration <- lm(duration ~ duration_real,
                     data = patch_summary_compare)

@@

```{r}
# make figure comparing different methods
figure_patch_duration <-
  ggplot()+
  geom_segment(data = patch_summary_compare,
               aes(x = 100,
                   xend = duration_real,
                   y = duration,
                   yend = duration),
               col = "grey")+
  geom_segment(data = patch_summary_compare,
               aes(x = duration_real,
                   xend = duration_real,
                   y = 100,
                   yend = duration),
               col = "grey")+
  geom_point(data = patch_summary_compare,
             aes(duration_real, 
                 duration),
             show.legend = F,
            size = 3,
            stroke = 1,
            shape = 21,
            fill = pal[2],
            col = "white")+
  geom_smooth(data = patch_summary_compare,
             aes(duration_real, 
                 duration),
             se = F,
             size = 0.5,
             col = pal[1],
             alpha = 0.2,
             method = "glm",
             show.legend = F)+
  annotate(geom = "text",
           x = 300, y = 900,
           size = 5,
           label = "R^2 == 0.845",
           parse = T)+
  scale_x_log10(breaks = c(300, 600, 900),
                labels = as.integer(c(300, 600, 900) / 60))+
  scale_y_log10(breaks = c(300, 600, 900),
                labels = as.integer(c(300, 600, 900) / 60))+
  coord_equal(expand = F,
              xlim = c(200, 1200),
              ylim = c(200, 1200))+
  ggthemes::theme_few()+
  labs(x = "duration (min)",
       y = "inferred duration (min)")
```

>>>>

```{r}
# read and plot example data
data <- fread("data/atlas1060_allTrials_annotated.csv")
data_raw <- copy(data)

# plot data
fig_data_raw <-
  ggplot(data)+
  geom_path(aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(aes(x, y),
             col = "steelblue", alpha = 0.2, size = 2)+
  ggthemes::theme_map()+
  coord_sf(crs = 32631)

@@

### Calculate residence time

```{r}
# load recurse
library(recurse)

# get recurse data for a 10m radius
data_recurse <- getRecursions(data_unproc[, list(x, y, time, TAG)],
                              radius = 200)
```

@@

```{r}
# get linear model
model_duration <- lm(duration_real ~ duration,
                     data = patch_summary_compare)

@@

```{r}
# make figure comparing different methods
figure_patch_duration <-
  ggplot()+
  geom_segment(data = patch_summary_compare,
               aes(x = 100,
                   xend = duration,
                   y = duration_real,
                   yend = duration_real),
               col = "grey")+
  geom_segment(data = patch_summary_compare,
               aes(x = duration,
                   xend = duration,
                   y = 100,
                   yend = duration_real),
               col = "grey")+
  geom_point(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             show.legend = F,
            size = 3,
            stroke = 1,
            shape = 21,
            fill = pal[2],
            col = "white")+
  geom_smooth(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             se = F,
             size = 0.5,
             col = pal[1],
             alpha = 0.2,
             method = "glm",
             show.legend = F)+
  annotate(geom = "text",
           x = 300, y = 900,
           size = 5,
           label = "R^2 == 0.849",
           parse = T)+
  scale_x_log10(breaks = c(300, 600, 900),
                labels = as.integer(c(300, 600, 900) / 60))+
  scale_y_log10(breaks = c(300, 600, 900),
                labels = as.integer(c(300, 600, 900) / 60))+
  coord_equal(expand = F,
              xlim = c(200, 1200),
              ylim = c(200, 1200))+
  ggthemes::theme_few()+
  labs(x = "inferred duration (min)",
       y = "real duration (min)")
```

### 2020-10-08 index.rmd

--- 
knit: "bookdown::render_book"
title: "A Rough Guide to Pre-processing High-Frequency Animal Tracking Data"
author: "Pratik R. Gupte and others"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::pdf_book
documentclass: book
# bibliography: [refs.bib]
biblio-style: apalike
link-citations: yes
github-repo: pratikunterwegs/atlas-best-practices
description: "Source code for a guide to pre-processing high-frequency tracking data."
---

>>>>

--- 
knit: "bookdown::render_book"
title: "A Rough Guide to Pre-processing High-Frequency Animal Tracking Data"
author: "Pratik R. Gupte and others"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::pdf_book
documentclass: book
bibliography: [references.bib]
biblio-style: apalike
link-citations: yes
github-repo: pratikunterwegs/atlas-best-practices
description: "Source code for a guide to pre-processing high-frequency tracking data."
---
